Sleep, relative to wake, increases both veridical and false memory in the DRM paradigm:

### 2023-07-25 manuscript.Rmd
Minor changes to fix procedure figure

if (!dir.exists('data')){dir.create('data')}
if (!dir.exists('Figures')){dir.create('Figures')}
```

```{r getdata, include=FALSE}
# download the data if not already present
osfproject <- osf_retrieve_node("9pdyf")
osffiles <- osf_ls_files(osfproject,path='Stage 2/Data/All the csv needed for Final_Analysis.Rmd')
if (!file.exists('data/full.csv')){
  hid <- pmatch('full.csv',as.character(unlist(osffiles[,1])))
  osf_download(osffiles[hid,], path='data/')
}
if (!file.exists('data/lure_final.csv')){
  hid <- pmatch('lure_final.csv',as.character(unlist(osffiles[,1])))
  osf_download(osffiles[hid,], path='data/')
}
if (!file.exists('data/studied_final.csv')){
  hid <- pmatch('studied_final.csv',as.character(unlist(osffiles[,1])))
  osf_download(osffiles[hid,], path='data/')
}
if (!file.exists('data/Table 2_Material.csv')){
  hid <- pmatch('Table 2_Material.csv',as.character(unlist(osffiles[,1])))
  osf_download(osffiles[hid,], path='data/')
}

@@

if (buildfigures==1){
#make boxes
immediate_group <- boxGrob(glue("Immediate Groups"),
                           txt_gp = gpar(col = "black", fontsize = 16),
                           box_gp = gpar(fill = 0, col = 0),
                           x = .25,
                           y = .93,
                           bjust = "center")

@@

ggdraw() +
  draw_image(image_sleep,
             x = 0.87,
             y = 0.4,
             width = 0.05,
             height = 0.05) +
  draw_image(image_wake,
             x = 0.67,
             y = 0.4,
             width = 0.05,
             height = 0.05)

>>>>

if (!dir.exists('data')){dir.create('data')}
if (!dir.exists('Figures')){dir.create('Figures')}

```{r getdata, include=FALSE}

# download the data if not already present
osfproject <- osf_retrieve_node("9pdyf")
osffiles <- osf_ls_files(osfproject,path='Stage 2/Data/All the csv needed for Final_Analysis.Rmd')
if (!file.exists('data/full.csv')){
  hid <- pmatch('full.csv',as.character(unlist(osffiles[,1])))
  osf_download(osffiles[hid,], path='data/')
}
if (!file.exists('data/lure_final.csv')){
  hid <- pmatch('lure_final.csv',as.character(unlist(osffiles[,1])))
  osf_download(osffiles[hid,], path='data/')
}
if (!file.exists('data/studied_final.csv')){
  hid <- pmatch('studied_final.csv',as.character(unlist(osffiles[,1])))
  osf_download(osffiles[hid,], path='data/')
}
if (!file.exists('data/Table 2_Material.csv')){
  hid <- pmatch('Table 2_Material.csv',as.character(unlist(osffiles[,1])))
  osf_download(osffiles[hid,], path='data/')
}

@@

#make boxes
immediate_group <- boxGrob(glue("Immediate Groups"),
                           txt_gp = gpar(col = "black", fontsize = 16),
                           box_gp = gpar(fill = 0, col = 0),
                           x = .25,
                           y = .93,
                           bjust = "center")

@@

ggdraw() +
  draw_image(image_sleep,
             x = 0.87,
             y = 0.36,
             width = 0.08,
             height = 0.08) +
  draw_image(image_wake,
             x = 0.665,
             y = 0.36,
             width = 0.08,
             height = 0.08)
